Synthesizing Random Generators via Higher-Order Representations

### 2019-01-16 paper/main.tex
Unfolded figure

If we use \megadeth to automatically derive a random generator for \ensuremath{\Conid{Exp}}, we
obtain a uniform generation probability distribution over constructors, i.e.,
$P(\ensuremath{\Conid{Val}}) = P(\ensuremath{\Conid{Add}}) = P(\ensuremath{\Conid{Mul}}) = 1/3$.
%
In this setting, $P(match(foo\#1))$ results $1/2430000$, meaning that, in
average, we will need to generate over than two million test cases in order to
be able to test the first clause of \ensuremath{\Varid{foo}} only once.
%
This situation can be somewhat improved if we decide to use \dragen to obtain a
random generator.
%
By optimizing the generation probabilities in order to benefit the generation of
\ensuremath{\Conid{Add}} constructor in a ratio of $20:1$ with respect to the rest of them, we
obtained a distribution of values where $P(match(foo\#1)) \approx 1/300000$.

%
Although this certainly improves the probability of generating a matching value,
this probability is not substantial enough to become practical.
%
Additionally, by favoring the generation probabilities towards the \ensuremath{\Conid{Add}}
constructor, we found that the probability of generating a value matching the
second clause of \ensuremath{\Varid{foo}} (which does not matches against it) also gets diminished
into an impractival value.

@@

@@

>>>>

If we use \megadeth to automatically derive a random generator for \ensuremath{\Conid{Exp}}, we
obtain a uniform generation probability distribution over constructors, i.e.,
$P(\ensuremath{\Conid{Val}}) = P(\ensuremath{\Conid{Add}}) = P(\ensuremath{\Conid{Mul}}) = 1/3$.
%
In this setting, $P(match(foo\#1))$ results $1/2430000$, meaning that, in
average, we will need to generate over than two million test cases in order to
be able to test the first clause of \ensuremath{\Varid{foo}} only once.
%
This situation can be somewhat improved if we decide to use \dragen to obtain a
random generator.
%
Using this tool, we can optimize the generation probabilities in order to
benefit the generation of some data constructors over the rest.
%
Considering that the first pattern matching of \ensuremath{\Varid{foo}} involves the data
constructor \ensuremath{\Conid{Add}} as the only recursive one, we can set an target generation
proportion of \ensuremath{\Conid{Add}} data constructors of, for instance, $20:1$ with respect to
the rest of the generated data constructors.
%
By doing so, the obtained distribution of values results such that
$P(match(foo\#1)) \approx 1/300000$.
%
Although this certainly improves the probability of generating a matching value,
this probability is not substantial enough to become practical.

Additionally, by favoring the generation probabilities towards the \ensuremath{\Conid{Add}}
constructor, we found that the probability of generating a value matching the
second clause of \ensuremath{\Varid{foo}} (which does not matches against it) also gets diminished
into an impractival value.

@@

\subsection{\textbf{Representing Pattern Matchings}}

@@

\subsection{\textbf{Representing Abstract Interfaces}}

### 2019-01-16 paper/sections/randomtesting.tex
Unfolded figure

If we use \megadeth to automatically derive a random generator for |Exp|, we
obtain a uniform generation probability distribution over constructors, i.e.,
$P(|Val|) = P(|Add|) = P(|Mul|) = 1/3$.
%
In this setting, $P(match(foo\#1))$ results $1/2430000$, meaning that, in
average, we will need to generate over than two million test cases in order to
be able to test the first clause of |foo| only once.
%
This situation can be somewhat improved if we decide to use \dragen to obtain a
random generator.
%
By optimizing the generation probabilities in order to benefit the generation of
|Add| constructor in a ratio of $20:1$ with respect to the rest of them, we
obtained a distribution of values where $P(match(foo\#1)) \approx 1/300000$.

%
Although this certainly improves the probability of generating a matching value,
this probability is not substantial enough to become practical.
%
Additionally, by favoring the generation probabilities towards the |Add|
constructor, we found that the probability of generating a value matching the
second clause of |foo| (which does not matches against it) also gets diminished
into an impractival value.

>>>>

If we use \megadeth to automatically derive a random generator for |Exp|, we
obtain a uniform generation probability distribution over constructors, i.e.,
$P(|Val|) = P(|Add|) = P(|Mul|) = 1/3$.
%
In this setting, $P(match(foo\#1))$ results $1/2430000$, meaning that, in
average, we will need to generate over than two million test cases in order to
be able to test the first clause of |foo| only once.
%
This situation can be somewhat improved if we decide to use \dragen to obtain a
random generator.
%
Using this tool, we can optimize the generation probabilities in order to
benefit the generation of some data constructors over the rest.
%
Considering that the first pattern matching of |foo| involves the data
constructor |Add| as the only recursive one, we can set an target generation
proportion of |Add| data constructors of, for instance, $20:1$ with respect to
the rest of the generated data constructors.
%
By doing so, the obtained distribution of values results such that
$P(match(foo\#1)) \approx 1/300000$.
%
Although this certainly improves the probability of generating a matching value,
this probability is not substantial enough to become practical.

Additionally, by favoring the generation probabilities towards the |Add|
constructor, we found that the probability of generating a value matching the
second clause of |foo| (which does not matches against it) also gets diminished
into an impractival value.
